A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-17 manuscript.Rmd
fix small typo

Git and GitHub can do even more to support you when collaborating with fellow researchers, for example, by providing a web interface to track issues and their status (open/closed/resolved) and further means to manage and merge multiple, parallel versions of code (such as branches, pull requests, or merges), but this is beyond the scope of this tutorial. In particular, GitHub's issue management can be leveraged as a post-publication platform to discuss manuscripts and their results [^1].
Another benefit of using Git and GitHub is that experimentation is highly encouraged since you can go back to any state quickly. Even when you lose access to the file on your computer, everything can be backed up on a remote git server. Further, one can reduce the liklihood of dead code accumulating (e.g., lines that have been commented out) because it is safe to simply remove unneeded code blocks and track their removal in Git.

@@

The flexibility to fully control the software environment is of particular interest for software infrastructures where users cannot install software because of limited access rights, for example, on cloud computing platforms or high-performance computing clusters. However, running docker needs unrestricted access rights to the system, which are rarely granted on those platforms. For this case, Singularity provides a fully compatible alternative (see Section under [Linux]) that can be executed with limited access rights.

>>>>

Git and GitHub can do even more to support you when collaborating with fellow researchers, for example, by providing a web interface to track issues and their status (open/closed/resolved) and further means to manage and merge multiple, parallel versions of code (such as branches, pull requests, or merges), but this is beyond the scope of this tutorial. In particular, GitHub's issue management can be leveraged as a post-publication platform to discuss manuscripts and their results [^1].
Another benefit of using Git and GitHub is that experimentation is highly encouraged since you can go back to any state quickly. Even when you lose access to the file on your computer, everything can be backed up on a remote Git server (like GitHub or GitLab). Further, one can reduce the liklihood of dead code accumulating (e.g., lines that have been commented out) because it is safe to simply remove unneeded code blocks and track their removal in Git.

@@

The flexibility to fully control the software environment is of particular interest for software infrastructures where users cannot install software because of limited access rights, for example, on cloud computing platforms or high-performance computing clusters. However, docker needs unrestricted access rights to the system, which are rarely granted on high-performance computing clusters. For this case, Singularity provides a fully compatible alternative (see Section under [Linux]) that can be executed with limited access rights.
